\input{syllabuspre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Syllabus}
\MYHEADERS{Syllabus}{}

\subsection*{Course Instructor}
Dr.\ Gregory M.\ Kapfhammer\\
\noindent Office Location: Alden Hall 108 \\
\noindent Office Phone: +1 814-332-2880 \\
\noindent Email: \url{gkapfham@allegheny.edu} \\
\noindent Twitter: \url{@GregKapfhammer} \\
\noindent Web Site: \url{http://www.cs.allegheny.edu/sites/gkapfham/} 

\subsection*{Instructor's Office Hours}

\begin{itemize}
	\itemsep 0em
	\item Monday: 1:00 pm -- 2:30 pm (30 minute time slots)
	\item Tuesday: 2:30 pm -- 4:00 pm (15 minute time slots)
	\item Wednesday: 4:30 pm -- 5:00 pm (15 minute time slots)
	\item Thursday: 9:00 am -- 10:00 am (15 minute time slots) {\em and} \\ \hspace*{.69in} 2:30 pm -- 4:00 pm (15 minute time slots)
	\item Friday: 1:00 pm -- 2:30 pm (10 minute time slots) {\em and} \\ \hspace*{.49in} 4:30 pm -- 5:00 pm (5 minute time slots)
\end{itemize}

\noindent
To schedule a meeting with me during my office hours, please visit my Web site and click the ``Schedule'' link in the
top right-hand corner. Now, you can browse my office hours or schedule an appointment by clicking the correct link and
then reserving an open time slot. 

\subsection*{Course Meeting Schedule}

Neither CMPSC 500 nor 501 have a set meeting time.  Instead, students are required to meet with the course instructor
during office hours for a total of 60 minutes.  These meetings must be scheduled through the instructor's reservation
system and documented on a meeting record that you submit on the last day of classes.

\subsection*{Course Catalogue Description}

\begin{quote}
A corequisite seminar for all students participating in the Internship Program.  Internship students enroll twice, once
prior to and once following the Internship. Computer Science 500 focuses on expectations and planning, leading to the
Internship Proposal required for all students planning an internship.  Computer Science 501 provides the opportunity for
students who have completed the Internship to prepare written and oral reports on the Internship experience. The
student, in consultation with the faculty of the Department of Computer Science, is responsible for arranging for an
acceptable internship.  The courses meet together weekly for one-half a semester. Credit: One semester hour for each
course. Prerequisites: Completion of at least two core courses.
\end{quote}

\subsection*{Course Objectives}

The students in CMPSC 500 will develop a list of internship and career resources, explore their internship and career
interests, and write a proposal for the internship that they will undertake. The course aims to help students
learn more about the field of computing and the positions that are available to computer scientists who graduate from
Allegheny College.  Overall, the course will provide a framework that enables a student to secure an interesting and
meaningful internship.

\noindent
The students in CMPSC 501 will develop a list of career resources, explore their career interests, write a final report
describing their internship, and give a public presentation about their internship.  This course gives
students who recently completed an internship a forum for sharing their experiences with the Allegheny College community.

\subsection*{Performance Objectives}

At the completion of either CMPSC 500 or 501, a student should be familiar with resources related to various facets of
internships and careers. Students should have skills that enable them to effectively investigate internships and
careers.  Also, the student should have a better understanding of the computer science sub-disciplines that they may
want to pursue after graduation from Allegheny College. Finally, students should also have improved their writing and
speaking skills.

\subsection*{Required Textbooks}

\noindent
There are no required textbooks for this class.  However, students who want to improve their technical writing skills
may consult the following books.

\noindent{\em BUGS in Writing: A Guide to Debugging Your Prose}. Lyn Dupr\'e. Second Edition,  ISBN-10: 020137921X,
ISBN-13: 978-0201379211, 704 pages, 1998.

\noindent{\em Writing for Computer Science}.  Justin Zobel. Second Edition,  ISBN-10: 1852338024, ISBN-13:
978-1852338022, 270 pages, 2004.

\subsection*{Grading Policy}

% Final Resume
% Two Page Career Interest Statement
% Two Page Description of Career Resources
% Secured Internship
% Two Page Internship Proposal
% 
% Students will be expected to "workshop" their resume with the Instructor and the staff in the Office of Career Services
% (OCS). Members of the Office of Career Services will be able to provide the student will invaluable advice concerning
% resumes, internship opportunities, and careers. A student's career interest statement must describe the types of careers
% in which a student is interested. However, this document should go beyond the basic statement of a job description and
% also include information about preferred geographical location, technologies that the student is interested in using,
% types of software the student would like to develop, etc. Each student will be responsible for the creation of a
% document that describes the career and internship resources that they found to be the most valuable. For example, a
% student might create a listing of different Web sites and books that they found useful. However, this listing should
% also include a description of the strengths and weaknesses of these resources. Finally, each student must secure an
% internship and write a short proposal (in conjunction with the staff members at their chosen company) to describe the
% work that they will conduct.
% 

The grade that a student receives in this class will be based on the following categories. All percentages are
approximate and it is possible for the assigned percentages to change during the academic semester if a need to do so
presents itself. 

Grade percentages for students in CMPSC 500:

\vspace{-.1in}
\begin{center}
\begin{tabular}{ll}
Class Participation and Instructor Meetings & 20\% \\
Career Interest Statement & 20\% \\
Description of Career Resources & 20\% \\
Internship Proposal & 30\% \\
Secured Internship & 10\% \\
\end{tabular}
\end{center}

Grade percentages for students in CMPSC 501:

\vspace{-.1in}
\begin{center}
\begin{tabular}{ll}
Class Participation and Instructor Meetings & 20\% \\
Internship Retrospective & 25\% \\
Description of Career Resources & 25\% \\
Internship Presentation & 30\% \\
\end{tabular}
\end{center}




Each of the above grading categories has the following definition:

\begin{itemize}

	\item {\em Class Participation and Instructor Meetings}: All students are required to actively participate during
		all of the class sessions. Your participation will take forms such as answering questions about the required
		reading assignments, asking constructive questions of your group members, giving presentations, and leading a
		discussion session. Furthermore, all students are required to meet with the course instructor during office
		hours for a total of sixty minutes during the Fall 2013 semester.  These meetings must be scheduled through the
		instructor's reservation system and documented on a meeting record that you submit on the day of the final
		examination. A student will receive an interim and final grade for this category.

	
\end{itemize}

\subsection*{Class Policies}

\subsubsection*{Disability Services}

The Americans with Disabilities Act (ADA) is a federal anti-discrimination statute that provides comprehensive civil
rights protection for persons with disabilities.  Among other things, this legislation requires all students with
disabilities be guaranteed a learning environment that provides for reasonable accommodation of their disabilities.
Students with disabilities who believe they may need accommodations in this class are encouraged to contact Disability
Services at 332-2898.  Disability Services is part of the Learning Commons and is located in Pelletier Library.
Please do this as soon as possible to ensure that approved accommodations are implemented in a timely fashion.

\subsubsection*{Honor Code}

The Academic Honor Program that governs the entire academic program at Allegheny College is described in the Allegheny
Course Catalogue.  The Honor Program applies to all work that is submitted for academic credit or to meet non-credit
requirements for graduation at Allegheny College.  This includes all work assigned for this class (e.g., examinations,
laboratory assignments, and the final project).  All students who have enrolled in the College will work under the Honor
Program.  Each student who has matriculated at the College has acknowledged the following pledge:

\begin{quote}
I hereby recognize and pledge to fulfill my responsibilities, as defined in the Honor Code, and to maintain the
integrity of both myself and the College community as a whole.  
\end{quote}

\end{document}
